A seamless, client-centric programming model for type safe web applications

### 2014-05-07 paper.tex
Fix "we're using Haskell!!" six pages into a Haskell Symposium paper.

\paragraph{Two compilers}
The principal trick to our solution is compiling the same program twice; once
with a compiler that generates the server binary, and once with one that
generates JavaScript. Conditional compilation is used for a select few
functions, to enable slightly different behavior on the client and on the
server as necessary. As we believe that a monadic programming style is a good
fit for this application, we have chosen to use Haskell as the base of our
solution, which by default leads us to choose GHC as our server side compiler.
For reasons outlined in section \ref{sec:haste}, the Haste compiler was chosen
to provide the client side code.

>>>>

\paragraph{Two compilers}
The principal trick to our solution is compiling the same program twice; once
with a compiler that generates the server binary, and once with one that
generates JavaScript. Conditional compilation is used for a select few
functions, to enable slightly different behavior on the client and on the
server as necessary. Using Haskell as the base language of our solution leads
us to choose GHC as our server side compiler by default. We chose the Haste
compiler to provide the client side code, mainly owing to our great familiarity
with it and its handy ability to make use of vanilla Haskell packages from
Hackage.
